\chapter{Early Buildings}

I urged Mr. C to go back to bed quickly. When passing the auditorium, I
accidentally rode past him and rode to the back of the auditorium.  We were
about to turn around and return, but we were surprised to find that there was a
trail behind the auditorium that led to the east side of the auditorium.
Because it was getting late, we didn't want to go around again. We were in a
hurry to go back at this time, so we rode on this trail without thinking too
much.

The path is paved with paving bricks and passes through the trees behind the
auditorium. If anything, it actually looks no different from the paths that
cross the lawn in front of Li Wenzheng Hall.  But as soon as I rode on the
trail, I had a subtle, strange feeling. I always felt like there was something
around me, but I couldn't see anything. I calmed down, hinting to myself that
this was just an illusion, and then concentrated on riding again.  When riding
to the exit, Mr. C in front suddenly screamed and braked suddenly. I was also
startled by him and almost bumped into him.  "What's wrong?" I asked casually,
then looked up and saw someone standing under the shade of a tree at the
intersection. Mr. C almost hit him just now. And that person looked at us both
in surprise.  I looked at the man from behind and felt that he looked familiar.
I moved forward and took a closer look and found that the man was Mr. O from
the same department.  I felt very strange and asked him why he was standing in
such a place so late. How dangerous it was.  "I also want to say that it's so
late, how did you get out of here? How could I have imagined that there are
people hanging around on bicycles at this time... So why are you hanging around
here in the middle of the night?" he returned.  I told him that we went to the
West Lake Swimming Pool to find out why the swimming pool was filled with
water.  After hearing this, his expression changed and he asked us if we had
encountered any strange phenomena.  I was stunned for a moment, not sure
whether I should tell him about the supernatural things in the West Lake
swimming pool, so I looked to Mr. C for advice. We exchanged glances and agreed
that Mr. O might know some information, so we decided to tell him about it and
told him in detail what we had seen in West Lake.

After listening to this, Mr. O nodded thoughtfully, and then asked us if we had
any strange feelings while crossing this trail.  We didn't understand what he
was referring to at first, and were stunned for a moment. Then we suddenly
remembered that we had indeed felt that there was something invisible around us
just now, so we told him how we felt at that time.  After hearing this, he
nodded again and fell into thought. After thinking for a while, he suddenly
raised his head and said to us: "That's all, you are involved in this kind of
thing anyway, so I will explain it to you as a senior in the industry."

From Mr. O’s explanation, we gradually learned about the unknown stories that
happened in this land.  It turns out that there is an ancient barrier in the
area of this old building complex, protecting the historic country of Hades.
In a sense, Hades belongs to a kingdom in another world, and people in this
world generally cannot see them. Ordinary people occasionally feel some chills
for no reason, and that is the limit of their perception of the people of the
underworld; only people with strong inspiration can see them clearly and even
communicate with them. Mr. O has a strong sense of inspiration, so he can feel
everything here.  The barrier protects the inhabitants of Hades and isolates it
from the outside world. However, in order to protect the life inside Hades,
Hades also needs to communicate with the outside world. Therefore, when
building the barrier, a passage was reserved. This passage will be opened at
midnight every day, and residents within the barrier can come out at this time.
, people from outside can also enter and trade with each other. And this
passage is the passage behind the auditorium that can be seen now.

It was getting late, so Mr. O advised us two newbies to go back early and take
us to learn the secrets of other places another day. So we agreed that in three
days, Mr. O would take us to visit the Hades.

\vfill

\paragraph{Diary} On June 23, the author and Mr. C were walking from Zero-Zero
Pavilion to Zicao Road and passed the auditorium. This was the first time in
four years that the author discovered that there was a trail behind the
auditorium.  When I first started thinking about it, I originally planned to
set the opening time of the passage from 7 to 9 pm, because when I passed by
this place that day, it was after 8 o'clock, which was the 12 o'clock hour,
that is, 7 to 9 pm.  However, after I officially started writing, when I
conceived the plot line, I placed the plot of passing the auditorium behind the
West Lake. In the plot, it was close to midnight when "we" left the West Lake,
so I changed the opening time of the passage to midnight.
