\chapter{Gong Office}

When we left West Lake that night, it was almost late at night, so we were
going to go back to the dormitory directly.  When we were riding by in front of
the I-shaped hall, we found that the lights were still on in front of the main
entrance of the I-shaped hall. The dim light shines on the closed red door,
making it look particularly strange.  Seeing this scene, I couldn't help but
think of a ghost story I had read before.  It is said that even in the summer
when the days are long and the nights are short, the Forbidden City must close
before 5 pm. The reason is that after the sun and the moon begin to take over,
the yang energy between the sky and the earth gradually becomes thinner and the
yin energy becomes stronger, and some people dare not see the light during the
day. Things will start to come out and move.  As the imperial palace of the
Ming and Qing dynasties, the Forbidden City has witnessed countless unsolved
and unsolved cases in the front and rear palaces over the past 400 years.
Therefore, at dusk, countless ghosts and ghosts come out to act, so for the
safety of tourists , the Forbidden City always ensures that it will close
before the sun goes down.

In order to not be the only one who was scared, I told Mr. C this ghost story,
but Mr. C actually told me a ghost story about the Gongzi Hall.  Since we
usually live in Tsinghua University, such a story is even more terrifying to a
certain extent.

It is said that at that time, lights were not lit in front of the Gongzi Hall
at night.  Once, a teacher worked overtime for a long time after get off work.
When he was about to leave after work, it was completely dark.  He hurriedly
packed up his things and went out, ready to leave. When he was going to drive,
he found that he had left his car keys in the office, so he went back to get
them.  However, when he came back from this trip and stepped through the door
of the G-shaped Hall, he found that his original office was gone. Behind the
door was a world he had never seen before.  Rows of traditional houses on the
top of hard hills are arranged along several parallel streets. There are two-
and three-story attics a little further away. Some of them even have platforms
downstairs, with storytellers, singers and dancers on the platforms. They all
performed excitedly.  Every house on the street is brightly lit, so prosperous!
The streets were full of strange people that I had never seen before. Some wore
strange masks, some had fox ears, and some covered themselves entirely with
robes, leaving only their faces exposed.  Although there were all kinds of
strange people, everyone was talking and laughing while wandering around the
street market.  There are vendors selling snacks on both sides of the street,
such as roasted chicken with sauce, duck and goose, mutton legs and pig ears,
stinky tofu, sesame seed jelly and water steamed buns, all of which are
complete; There are also all kinds of gadgets, including windmills that can
turn without wind, stones that light up by themselves, hats that get bigger and
smaller, and so on.  The street was crowded with people. In addition to people
shopping, there were also people who came out of the store to solicit
customers. They diligently handed out advertisements printed on big red paper
to tourists, telling the various wonderful things about the store.  He was
stunned for a moment, and hurriedly wanted to exit, when he saw a figure flying
past him quickly and passing through the door.  He couldn't help being
startled, and when he looked up, he realized that there was someone flying in
the air.  The figure of the person flying in the air seems a bit ethereal, a
bit transparent, and seems to be real and illusory, as if it will dissipate in
the next second, and the closer to the feet, the more transparent and blurry it
becomes. If many people's feet are not focused carefully, If you look, you
can't see it at all.  Looking into the sky in the distance, there seems to be
an island floating in the sky, but it seems to be separated by a layer of fog,
so it is really hard to see clearly.  At this time, the teacher was deeply
aware that he had broken into someone else's world this time, and he couldn't
help but feel nervous, wondering if he could go back safely. Thinking of Fei
Ling who just walked out of the door, he couldn't help but guess that this door
was the passage connecting the two worlds.  After thinking about it, he
hurriedly exited through the door and found that the I-shaped Hall was indeed
the same G-shaped Hall, and the Tsinghua Garden was indeed the same Tsinghua
Garden.  With some confidence in his heart and the mentality of giving it a
try, he stepped through the door again. Sure enough, it was still the strange
and strange world. When he exited, he was still in the Tsinghua University
Garden in the middle of the night.  This door has indeed become a passage
between this world and another world.  The teacher had some unspeakable
emotions in his heart and had nowhere to express them. He just hurriedly walked
into the G-shaped hall through the small side door, took the key, and left. He
secretly vowed never to work overtime in the G-shaped hall again.  And from
then on, lights were lit in front of the I-shaped hall at night, and teachers
began to only use the small door next to them when entering and leaving.  Rumor
has it that this teacher raised the matter at the school council meeting, so in
order to keep a distance from strange forces and chaotic gods, the Gongzi
Office formed such a practice.

When Mr. C finished speaking, we happened to ride next to the second religion.
The Second Sect is not open for self-study on weekdays, and the whole building
is dark late at night. Now there is a circle outside to block it, which makes
it even more desolate.  Moved by this atmosphere, I suddenly thought of the
widely circulated ghost stories of the Second Religion, and I couldn't help but
feel a chill in my body, so I urged Mr. C to leave this land of right and wrong
quickly.

\vfill

\paragraph{Diary} On June 23, after the author and Mr. C found Zero-Zero
Pavilion, they planned to go to Zicao to talk about it again. I was riding by
the I-shaped Hall and found that the door of the I-shaped Hall was still lit at
night. The lights were dim, making it look a little eerie and mysterious.
