\chapter{The Phantom of the West Lake}

On the southwest side of the lotus pond in Jinchun Garden, a "West Lake
Swimming Pool" was built.  In normal years, this place is very lively in the
summer, with many people coming here to swim; in the winter, water is released
to make ice, and an ice rink is opened up; in addition, I heard that the winter
swimming team trains here.  However, during the epidemic, there were really few
people in the school. I remember that when there were fewer people swimming and
skating, the West Lake was no longer open to the public, and the swimming pool
no longer contained water. However, when I passed by the West Lake that day, I
found that there was water in the swimming pool. Full of water, I was deeply
puzzled, so I made an appointment with Mr. C to find out in my spare time.

That evening, after dinner, Mr. C and I went outside the West Lake together.
Not far from the west side of the West Lake is Jinchun Road; on the south side
is Qinghua Road; on the east side is a small canal, and across the canal are
hills with lush trees; on the north side is the mountain, where we just visited
a few days ago Ling Ling Pavilion. The swimming pool is surrounded by iron
railings.  The murder case a few days ago and the legend of the Lotus Fairy
still made us both very scared, so we didn't dare to go too far into the
forest. We just walked around and observed the fence of the swimming pool.

We walked around the boundary of the West Lake and found that the gate was
closed and the entire swimming pool was deserted and eerily quiet. The
strangely clear water in the pond was so silent that there was no ripple at
all. There seems to be no life here except for the occasional crow of crows
from the trees and the occasional pedestrian passing by on Tsinghua Road.  The
sky was gradually getting darker, and the sound of people humming, singing and
dancing seemed to come from the distant lotus pond, but it was still deathly
silent here.  We turned around again and again, but still found nothing. At
this time, an idea suddenly flashed through my mind, and I wanted to encourage
Mr. C to climb over the railing and take a look, but after thinking about it, I
decisively gave up the idea. Firstly, it was a bit dangerous. Secondly, if he
was discovered, I don’t know what would happen. What consequences? It's really
not worth the punishment for this matter in the last year. Now that I have
given up the idea of further exploration, I plan to go back with Mr. C.

However, at this moment, there seemed to be some sound of water stirring in the
swimming pool. We looked quickly and found that the originally calm lake had a
series of ripples for some reason, like a boat passing by, but I was not there.
See anything on the water.  "Is there anything there?" I asked Mr. C quietly,
but Mr. C only shook his head, indicating that he didn't see anything. "No
way... is this haunted?" I was a little frightened.  The invisible thing in the
water seemed to be still swimming, leaving a long trail on the water.  The
transparent thing swam for a while and returned to the shore. Then the
originally dry ground by the pool became wet, and the sound of wet feet
stepping on the ground could be heard. It seemed that it had landed.  The
footprints left by the water began to extend to the south of the swimming pool,
until they reached the southernmost edge of the swimming pool. They turned west
again, and then walked all the way to the main entrance and stopped.  After a
while, a lot of water suddenly splashed on the south side of the pond,
accompanied by the sound of water entering. Then I saw waves rising on the
water, making ripples, as if many people were racing to swim. .  Night has
completely fallen, and the distant music has disappeared without a trace.
Gradually, we can no longer see clearly what is happening on the water. We can
only hear the sound of paddling and waves constantly coming from the pond.
Today was really an eye-opener. Mr. C and I looked at each other and saw the
fear in each other's eyes. We couldn't help but reveal a wry smile in tacit
understanding, and then quietly left on Tsinghua Road in the south.

\vfill

\paragraph{Diary} On the evening of June 23, while looking for Zero-Zero
Pavilion with Mr. C, I passed by the West Lake and found that the West Lake
swimming pool was filled with water. Since no one in the school should be using
the swimming pool during the epidemic, I was very confused.
